A unified model for parsing and sentence understanding

### 2016-03-14 writing/hard_stack_paper/paper.tex
TODO tweaks.

@@

\result{[SB] Patterns in the examples that the tree model got right that the LSTM didn't}

>>>>

\subsection{Parsing performance}

\todo{[AR] Fill in some details here.}
\todo{[SB] Read AR's report and work out what to include.}

@@

\question{What kind of error analysis would be interesting for this model?}

\result{[SB] Compare the types of errors in the different runs.}
